---
title: "MSDRCapstone Package"
author: "Cheng-Chung Li"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MSDRCapstone Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Installing necessary packages
```{r}
library(dplyr)
library(readr)
library(stringr)
library(stringi)
```

## Accessing the package
```{r}
library(devtools)
install_github("askia318/MSDRCapstone")
library(MSDRCapstone)
```

## Introduction 
The overall goal of the capstone project is to integrate the skills you have developed over the courses in this Specialization and to build a software package that can be used to work with the NOAA Significant Earthquakes dataset.

## eq_clean_data
This function takes raw NOAA data frame and returns a clean data frame. The clean data frame should have the following:
A date column created by uniting the year, month, day and converting it to the Date class
LATITUDE and LONGITUDE columns converted to numeric class

An example: 
```{r}
eq_clean_data()
```

## eq_location_clean
It cleans the LOCATION_NAME column by stripping out the country name (including the colon) and converts names to title case (as opposed to all caps).

```{r}
eq_location_clean()
```

## eq_map() 
It takes an argument data containing the filtered data frame with earthquakes to visualize. 

## eq_create_label() 
It takes the dataset as an argument and creates an HTML label that can be used as the annotation text in the leaflet map.
